
\documentclass[a4paper,10pt]{article}
\usepackage{latexsym,amssymb,amsmath}
\usepackage{titlesec}
\usepackage[top=1.2cm, bottom=1.2cm, left=1.2cm, right=1.2cm]{geometry}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{left=0em, label=--, topsep=0pt}

\begin{document}

    \begin{center}
    {\LARGE \textbf{Gandholi Sarat}}\\
    \vspace{2pt}
    \textit{M.Tech in Computer Science (Ongoing)} \\
    \vspace{6pt}
    \faPhone~\underline{+91 7730834575}   ~ ~
    \faEnvelope~\href{mailto:gandholisarat@gmail.com}{\underline{gandholisarat@gmail.com}} ~ ~
    \faLinkedin~\href{https://www.linkedin.com/in/gandholi-sarat}{\underline{linkedin.com/in/gandholi-sarat}} ~ ~
    \faGithub~\href{https://github.com/GandholiSarat}{\underline{github.com/GandholiSarat}} ~ ~
    \faLink~\href{https://gandholisarat.vercel.app}{\underline{gandholisarat.vercel.app}}
\end{center}


\vspace{4pt}

\section*{Summary}
Enthusiastic Computer Science student currently pursuing a M.Tech in Computer Science. Exploring binary instrumentation tools (DynamoRIO, PIN). Passionate about problem-solving, team collaboration, and continuous learning.

\section*{Education}

\noindent
\textbf{Sri Sathya Sai Institute of Higher Learning, Prashanthi Nilayam} \hfill \textbf{2025 -- Present} \\
\textit{M.Tech in Computer Science (Ongoing)} \\
\textit{Prasanthi Nilayam, Andhra Pradesh}
\vspace{4pt}

\noindent
\textbf{Sri Sathya Sai Institute of Higher Learning, Prashanthi Nilayam} \hfill \textbf{2023 -- 2025} \\
\textit{M.Sc. in Mathematics (Specialization in Computer Science)| CGPA: \textbf{8.6 (Distinction)}} \\
\textit{Prasanthi Nilayam, Andhra Pradesh} 
\vspace{4pt}

\noindent
\textbf{Sri Sathya Sai Institute of Higher Learning, Brindavan Campus} \hfill \textbf{2020 -- 2023} \\
\textit{B.Sc. (Hons.) in Mathematics | CGPA: \textbf{8.0 (Distinction)}} \\
\textit{Bengaluru, Karnataka} \\[6pt]

\section*{Project Experience}

\noindent
\textbf{DynamoRIO Memtrace Optimization} \\
\textit{Optimized memory tracing tool using DynamoRIO} \\
Improved trace collection in memory-intensive environments by applying buffer adjustments, address offset usage, and compression techniques. Benchmarked using FileBench, LMbench, and STREAM. \\
\faGithub~\href{https://github.com/GandholiSarat/DynamoRIO-Custom-Client}{\textbf{GitHub Repository}}


\vspace{4pt}

\noindent
\textbf{Binary Instrumentation Exploration} \\
\textit{Architecture Study of DynamoRIO and Intel PIN} \\
Explored DynamoRIO’s internal design and plugin system. Developed basic instrumentation tools and compared its features and usability with Intel PIN.

\vspace{4pt}

\noindent
\textbf{Unity Game Project – InnerGenius} \\
\textit{Game Design using Unity and C\#} \\
Created a game prototype aimed at enhancing decision-making and emotional intelligence through interactive challenges. \\
\faGamepad~\href{https://play.unity.com/en/games/a6df88fa-e4ba-4167-908b-4fd1285dfc5e/innergenius}{\textbf{Play Link: InnerGenius}}

\section*{Core Skills}
C/C++, Python, C\#, Algorithm Design, Computer Architecture, Unity, DynamoRIO, Intel PIN, Linear Algebra, Statistics

\section*{Additional Skills}
Real Analysis, Group Theory, Topology, Calculus

\section*{Languages}
English (Fluent), Telugu (Native)

\section*{Soft Skills}
Reading, Critical Thinking, Public Speaking, Rational Thinking, Emotional Intelligence

\end{document}